\documentclass[a4paper, oneside, 8pt, final]{amsart}

\usepackage{xeCJK}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
% \usepackage[babel=true,kerning=true]{microtype}

\usepackage{amsmath, amssymb}
\usepackage{eucal}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{amsaddr}
\usepackage{standalone}
\usepackage{caption}

\usepackage{stmaryrd}
\usepackage[noend]{algpseudocode}

\usepackage{tikz}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{arrows}
\usetikzlibrary{fit}
\usetikzlibrary{backgrounds}
\usetikzlibrary{positioning}
\usetikzlibrary{decorations.pathmorphing}
\usetikzlibrary{arrows.meta}

\def\osrank{\textsc{\small{osrank}}}
\def\Oscoin{\textsc{\small{Oscoin}}}
\def\oscoin{\textsc{\small{oscoin}}}
\def\netgraph{\mathcal{N}}
\def\accounts{\mathcal{A}}
\def\state{\mathcal{S}}
\def\ledger{\mathcal{L}}
\def\contributors{\mathcal{C}}
\def\projs{\mathcal{P}}
\def\miners{\mathcal{M}}
\def\registry{\mathcal{R}}
\def\bal{\mathsf{bal}}
\def\depend{\mathsf{depend}}
\def\undepend{\mathsf{undepend}}
\def\seedset{\Upsilon}
\def\epoch{\kappa}
\def\pagerank{PageRank}
\def\protocol{\Phi}

\newcommand{\tuple}[1]{\langle#1\rangle}
\newcommand{\mathsc}[1]{\text{\normalfont\scshape#1}}
\newcommand{\dep}{\xrightharpoondown[e]{d}}
\newcommand{\tx}[2]{\mathsf{#1}\lparen#2\rparen}
\newcommand{\field}[2]{#1_{\mathsf{#2}}}
\newcommand{\fn}[2]{\operatorname{#1}(#2)}
\newcommand{\prop}[2]{#1.{\mathrm{#2}}}

\newcommand*\eg{e.g.\ }
\newcommand*\ie{i.e.\ }

\algrenewcommand\algorithmicprocedure{\textbf{handler}}

% No paragraph indentation after section headers.
\makeatletter
\let\@afterindenttrue\@afterindentfalse
\makeatother

\newenvironment{fig}
  {\par\noindent\minipage{\linewidth}}
  {\endminipage\bigskip}

\newenvironment{epigraph}[2][]
{\leftskip=1cm \def\epigraph@author{#2} \smallskip\itshape}
{\par\vspace{0.5em}\normalfont\hfill---\ \Small\epigraph@author\hspace*{0.2cm}\par\medskip}
\makeatother

\setlist[description]{leftmargin=0.8cm, labelindent=\parindent}
\setlist[itemize]{leftmargin=0.8cm, labelindent=\parindent}
\setlist[enumerate]{leftmargin=0.8cm, labelindent=\parindent}

\setlength{\textwidth}{\paperwidth}
\addtolength{\textwidth}{-4cm}
\setlength{\textheight}{\paperheight}
\addtolength{\textheight}{-4cm}
\addtolength{\footskip}{\baselineskip}

\raggedcolumns
\calclayout

\makeatletter
\let\@wraptoccontribs\wraptoccontribs
\makeatother

\begin{document}

\title[open source coin]{open source coin \\ \vspace{0.5em}\Small{开源社区的信任和可持续性} \\ {\tiny Draft 4.0}}
\author{\Small Alexis Sellier\textsuperscript{$\dagger$} \qquad Eleftherios Diakomichalis\textsuperscript{$\dagger$} \qquad James Haydon\textsuperscript{$\dagger$}}
\date{February 2019}

\thanks{\textsuperscript{$\dagger$}Monadic, \texttt{\{alexis,ele,james\}@monadic.xyz}}

\begin{abstract}
开源运动的成功植根于点对点的分布态势和个体与个体的协作耦合。开源，诚然已从软件开发的理想主义孤篱生长成行业标准的高阁，但缺乏可持续的融资手段仍是横亘在此的负重。在这里，我们提议采用点对点协议创造的开源社区货币(\textsc{oscoin})，帮助我们一同开创可持续的，自由的开源软件经济。
\end{abstract}

\maketitle

\setlength{\columnsep}{1cm}
\begin{multicols}{2}

\input{sections/01-background.tex}
\input{sections/02-oscoin.tex}
\input{sections/03-osrank.tex}
\input{sections/04-ledger.tex}
\input{sections/05-smart-contracts.tex}
\columnbreak
\input{sections/06-applications.tex}
\pagebreak
\input{sections/07-future-work.tex}

\section*{致谢}
感谢Sam Hart帮助解决本文中的一些核心问题，谢谢他给出的宝贵想法与意见。感谢Aaron Levin在最初构思\oscoin{}时发人深省的一些讨论和做出的贡献。最后由衷感谢Monadic团队和我们的同事，你们对这项工作给予的支持与反馈是无价的。

\begin{thebibliography}{9}

\bibitem{bitcoin} Nakamoto, Satoshi. Bitcoin: A Peer-to-Peer Electronic Cash
  System. May 2009

\bibitem{ethereum} Wood, Gavin. Ethereum: A Secure Decentralised Generalised
  Transaction Ledger. December 2018

\bibitem{filecoin} Protocol Labs. Filecoin: A Decentralized Storage Network.
  July 2017

\bibitem{roads and bridges} Eghbal, Nadia. Roads and Bridges. The Unseen labor
  behind our digital infrastructure. July 2016.

\bibitem{pagerank} Brin, S.; Page, L. (1998). The anatomy of a
  large-scale hypertextual Web search engine (PDF). \emph{Computer Networks
  and ISDN Systems.} 30: 107–117.

\bibitem{pagerank-sybil} Cheng, A. and Friedman, E. 2006. Manipulability of
  PageRank under Sybil strategies. In First Workshop on the Economics of
  Networked Systems (NetEcon06).

\bibitem{trustrank} Z. Gyöngyi, H. Garcia-Molina, J. Pedersen: Combating Web
  Spam with TrustRank

\bibitem{incr pagerank} Bahmani, Bahman and Chowdhury, Abdur and Goel,
  Ashish. Fast Incremental and Personalized PageRank. Proc. VLDB
  Endow. December 2010.

\bibitem{nix} Dolstra, E., de Jonge, M. and Visser, E. Nix: A Safe and
  Policy-Free System for Software Deployment. In Damon, L. (Ed.), 18th Large
  Installation System Administration Conference (LISA '04), pages 79–92, Atlanta,
  Georgia, USA. USENIX, November 2004.

\end{thebibliography}

\end{multicols}
\end{document}
